Global patterns of forest autotrophic carbon fluxes

### 2020-03-01 manuscript/manuscript draft.Rmd
worked on methods (finished revision)

The effects of latitude and climate on FACF were analysed using mixed effects models using the package 'lme4' [@bates_fitting_2015] in R v.3.5.1 [@r_core_team_r:_2018]. The basic model for all analyses included a fixed effect of latitude or climate and a random effect of plot nested within geographic area. Geographic areas--*i.e.*, spatially clustered sites--are defined within ForC using a hierarchical cluster analysis on the distance matrix of the sites and a cutoff of 25km [@anderson-teixeira_forc_2018]. We experimented with inclusion of altitude as a fixed effect, but excluded it from the final models because it added very little explanatory power--that is, the change in AIC was generally small (often <2) relative to models excluding altitude. Hypotheses were accepted if the AIC difference ($\Delta$AIC) between a model including the fixed effect of interest and a corresponding null model excluding that fixed effect exceeded 2.0. All $R^2$ values presented here are marginal $R^2$ values, and refer to the proportion of variation explained by only the fixed effects, **unless otherwise specified**. **Becky, are there any instances of this?** Specific analyses are as described below.

@@

{**Note from Helene on the following paragraph: this makes it sound like analyses from H3 were about variation remaining after accounting for temperature, but analyses below don't seem to do that.**}  
**work on this paragraph**  
To investigate the potential joint and interactive effects of climate variables on carbon fluxes, multivariate models were also specified. We explored a large range of climate variable combinations and ultimately decided to focus on MAT and MAP. We favored these over variables with similar explanatory power because they are the most commonly reported climate variables and are recorded in ForC. MAT was consistently among the best individual predictors of FACF (Table S2), although it was occasionally out-performed by closely correlated climate variables (Fig. S2). In combination with MAT as a primary climate variable, MAP was consistently among the best secondary climate variables. Specifically, compared again a model including MATxMAP, there were no other variables that, in interaction with MAT, improved AIC by >2.0 and r-squared by >0.05.

**work on this paragraph**  
Models were run for total annual flux against annual climate variables, and for fluxes standardized by growing season length, defined as annual flux/length of growing season, against growing season climate variables. For analyses on data within the growing season, only linear models were specified.

>>>>

The effects of latitude and climate on FACF were analysed using mixed effects models using the package 'lme4' [@bates_fitting_2015] in R v.3.5.1 [@r_core_team_r:_2018]. The basic model for all analyses included a fixed effect of latitude or climate and a random effect of plot nested within geographic area. Geographic areas--*i.e.*, spatially clustered sites--are defined within ForC using a hierarchical cluster analysis on the distance matrix of the sites and a cutoff of 25km [@anderson-teixeira_forc_2018]. We experimented with inclusion of altitude as a fixed effect, but excluded it from the final models because it added very little explanatory power--that is, the difference in AIC ($\Delta$AIC) relative to models excluding altitude was generally small (often $\Delta$AIC<2). Hypotheses were accepted if the $\Delta$AIC between a model including the fixed effect of interest and a corresponding null model excluding that fixed effect exceeded 2.0. All $R^2$ values presented here are marginal $R^2$ values, and refer to the proportion of variation explained by only the fixed effects, **unless otherwise specified**. **Becky, are there any instances of this?** Specific analyses are as described below.

@@

To investigate the potential joint and interactive effects of climate variables on carbon fluxes, multivariate models were also specified. We explored a large range of climate variable combinations and ultimately decided to focus on MAT and MAP. We favored these over variables with similar explanatory power because they are the most commonly reported climate variables and are recorded in ForC. MAT was consistently among the best individual predictors of FACF (Table S2), although it was occasionally out-performed by closely correlated climate variables (Fig. S2). In combination with MAT as a primary climate variable, MAP was consistently among the best secondary climate variables. Specifically, compared again a model including MAT x MAP, there were no other variables that, in interaction with MAT, improved AIC by >2.0 and $R^2$ by >0.05. In examinging the joint and interactive effects of climate variables, an additive model including MAT and MAP as fixed effects was accepted when $\Delta$AIC >2 relative to a null including only MAT as a fixed effect. An interactive model including an MAT x MAP interaction was accepted when $\Delta$AIC >2 relative to a null including MAT and MAP as fixed effects.

To test whether and how FACF varied with climate when standardised by growing season length (Q5), we first standardized FACF by dividing by growing season length (as defined above). We then tested for correlations between growing season length-standardised FACF against growing season climate variables. For analyses on data within the growing season, only linear models were specified.
